A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-29 Simulator/article.tex
la2pdf commit - 2015:10:29	11:01:10	(Thu29.Oct)

One of the major shortcomings of autonomous underwater vehicles (AUVs) is their lack of intelligence. When encountering an interesting object, an AUV mounted with a sonar imaging system should be able to tell that this object might be worth closer examination, and act accordingly. This is challenging as what we deem as interesting is often something that stand out form the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.

>>>>

One of the major shortcomings of autonomous underwater vehicles (AUVs) is their lack of intelligence. When an AUV equipped with a sonar encounter an interesting object, it would be very beneficial if adapted its behavior to examine the object further. This is challenging as what we deem as interesting is often something that stand out form the background, i.e. it relies on previous knowledge. It would also need to process this information is near real-time to act in an efficient manner.
